Bird beak's elaboration and exploration

### 2021-08-10 Analysis/07-benchmarking.Rmd
Update 07-benchmarking.Rmd

```{r, eval = TRUE}
## Initialising the results result table
system(paste("echo \"thin, iterations, dimensions, time, d_time, r_time, size, d_size, r_size\" > recording.csv"))

@@

```{r, eval = TRUE}
## Initialising the results result table
system(paste("echo \"thin, iterations, dimensions, time, d_time, r_time, size, d_size, r_size\" > recording2.csv"))

## Running the test
for(dim in 2:17) {
  test.params(dimensions = dim, thin = 1000, nitt = 10000)
}
```

```{r}
## Upload the table
rable <- read.csv("recording2.csv")

par(mfrow = c(2,1))
plot(NULL, xlim = c(1, 5), ylim = range(run_time), main = "Run time", xlab = "10s of samples (per 10k iterations)", ylab = "log elapsed seconds")
for(i in 1:(nrow(rable)/5)) {
  lines(run_time[(1+5*(i-1)):(5+5*(i-1))], col = cols[i])
}

plot(NULL, xlim = c(1, 5), ylim = range(run_size), main = "Object size", xlab = "10s of samples (per 10k iterations)", ylab = "log bytes")
for(i in 1:(nrow(rable)/5)) {
  lines(run_size[(1+5*(i-1)):(5+5*(i-1))], col = cols[i])
}
```

>>>>

```{r, eval = FALSE}
## Initialising the results result table
system(paste("echo \"thin, iterations, dimensions, time, d_time, r_time, size, d_size, r_size\" > recording.csv"))

@@

```{r, eval = FALSE}
## Running the test
for(dim in 2:17) {
  test.params(dimensions = dim, thin = 1000, nitt = 10000)
}
```

```{r}
## Upload the table
rable <- read.csv("recording.csv")
rable_1k <- rable[1:80, ]
rable_10k <- rable[-c(1:80), ]

## Log values
run_time_1k <- rable_1k[, "time"]
run_size_1k <- rable_1k[, "size"]
run_time_10k <- rable_10k[, "time"]
run_size_10k <- rable_10k[, "size"]

cols <- rainbow(16)

par(mfrow = c(2,2))
plot(NULL, xlim = c(1, 5), ylim = range(run_time_1k), main = "Run time", xlab = "iterations (thin = 100)", ylab = "elapsed seconds", xaxt = "n")
axis(1, at = c(1:5), labels = seq(from = 1000, to = 5000, by = 1000))
for(i in 1:(nrow(rable_1k)/5)) {
  lines(run_time_1k[(1+5*(i-1)):(5+5*(i-1))], col = cols[i])
}

plot(NULL, xlim = c(1, 5), ylim = range(run_time_10k), main = "Run time", xlab = "iterations (thin = 1000)", ylab = "elapsed seconds", xaxt = "n")
axis(1, at = c(1:5), labels = seq(from = 10000, to = 50000, by = 10000))
for(i in 1:(nrow(rable_10k)/5)) {
  lines(run_time_10k[(1+5*(i-1)):(5+5*(i-1))], col = cols[i])
}

plot(NULL, xlim = c(1, 5), ylim = range(run_size_1k), main = "Object size", xlab = "iterations (thin = 100)", ylab = "bytes", xaxt = "n")
axis(1, at = c(1:5), labels = seq(from = 1000, to = 5000, by = 1000))
for(i in 1:(nrow(rable_1k)/5)) {
  lines(run_size_1k[(1+5*(i-1)):(5+5*(i-1))], col = cols[i])
}

plot(NULL, xlim = c(1, 5), ylim = range(run_size_10k), main = "Object size", xlab = "iterations (thin = 1000)", ylab = "bytes", xaxt = "n")
axis(1, at = c(1:5), labels = seq(from = 10000, to = 50000, by = 10000))
for(i in 1:(nrow(rable_10k)/5)) {
  lines(run_size_10k[(1+5*(i-1)):(5+5*(i-1))], col = cols[i])
}
```
